---
title: "ARMAPredictions"
author: "cyber-atlas"
date: "4/28/2019"
output: html_document
---


```{r}
library('quantmod')
library(tidyquant)
library('forecast')
library('ggplot2')
```

First we will start out by getting the symbols that we need

Let's look at how the S&P500 has been doing over the past year

```{r}
getSymbols("SPY", src="yahoo", from="2019-01-01")
getSymbols("AAPL", src="yahoo", from="2019-01-01")

AMD
```

Let's visualize the chart

```{r}
chartSeries(SPY)
```

Let's calculate the returns each day from the stock as a percentage and show the last 10 days of returns. 

```{r}
Returns <- diff(SPY$SPY.Close)/lag(SPY$SPY.Close, k=1)*1000
tail(Returns, 10)
```

Let's plot a histogram of the returns to visualize how well it performs

```{r}


Returns<-fortify(Returns)

ggplot(Returns, aes(x=SPY.Close) )+
  geom_histogram(binwidth = 2, color="black",fill="white",center=0)+ 
  scale_x_continuous(breaks=seq(-26, 36, 2))+
  geom_vline(xintercept = 0, col = 'darkred')+
  scale_y_continuous(breaks=seq(-1, 18, 2))+
  ggtitle("Frequency of Daily Percentage Change")+
  xlab("Percentage Difference")+
  ylab("Number of Occurances")

#hist(Returns)

```

** A bit of background ** 

A common way to prediction method used to predict values in a time series (in our case dates) is the Autoregressive Integrated Moving Average (ARIMA) model. 

ARIMA(P,D,Q)

AR stands for autogregressive, menaing it checks how much a variable correlates with itself. (P)

MA - A moving average of values you are using. 20 is a pretty common one for stocks (Q)

I - Degree of differencing needed to make the data stationary. Ex: degree of 1 replaces every value with the value minus the previous. Or degree 2, gets the difference of the difference (D)

The data needs to be stationary, basically needs to be horizontal, and one way to test is the Dicky Fuller test. 

To make the data stationary you can take the log of the price, then do the differences of the log values.  

When looking at the test, check that the p value is well under .5.

When forcasting a stock we can see with accuracy tomorrow's price within a few cents with relatively high accuracy. This is useful for Swing Traders and Day Traders who rely on the market to move just a little bit in either direction and take their money out. 

**What we did**

Here we decide to use the auto arima function. It looks for the best possible model to fit the data for us. 
```{r}
arimaData <- auto.arima(SPY$SPY.Close)
arimaData
```
Plot it

```{r}
chartSeries(as.ts(SPY$SPY.Close))
lines(fitted(arimaData), col='red')
```

As we can see the lines fit together pretty well

Let's try to forecast the date

```{r}
# fit.forecast <- forecast.Arima(arimaData)
fit.forecast <- forecast(arimaData)
fit.forecast
```

```{r}

plot(fit.forecast, ylab="Price", xlab="Trading Day in 2019. 4/26 was the 80th Day")
# Now, define a custom axis

# text(wt, mpg, row.names(mtcars), cex=0.6, pos=4, col="red") 

```

Source
The main source I used was R for Data Science Cookbook By YuWei Chiu

