---
title: "BollingerBands"
author: "cyber-atlas"
date: "April 23, 2019"
output: html_document
---
 
```{r}
# install.packages("quantmod")
library('quantmod')
library('ggplot2')
# install.packages("magrittr")
library('magrittr')
# install.packages("tidyquant")
library('tidyquant')
```

Getting the data

```{r}
#Define start and End dates
start <- as.Date("2018-04-25")
end <- as.Date("2019-04-25")
getSymbols(c("AAPL", "AMD", "SPY", "MU"), src="yahoo", from = start, to = end)

```

Bollinger bands are fundamentally based on the simple moving average, so lets get that

```{r}
#Charts the prices of the SPY 500
candleChart(SPY, up.col="green", dn.col="red", theme="white")
#Adds the simple moving average
plot(addSMA(n = 20))

#Extract taht data
#use function lines t
```

```{r}

candleChart(SPY, up.col="green", dn.col="red", theme="white")
addMACD()
```


```{r}

candleChart(SPY, up.col="green", dn.col="red", theme="white")
#Adds Bollinger Bands
addBBands()



```

```{r}
chartSeries(AMD, type='candlesticks')

```


We want to see if tidyquant will be a cleaner way of doing things

```{r}
#Trying a differnt (cleaner way to get the data)
SPY2 <- tq_get("SPY")

# SPY2 %>%
#     tq_mutate(x_fun = Cl, mutate_fun = SMA, n = 20) %>%
#     rename(SMA.20 = SMA)

# Had a bunch of issues with the mutate functions that were provided by the library
# unzip(A)
SPY2 %>%
    mutate(SMA.close = SMA(unlist(SPY2[,2]), n=20)) %>%


# 
# # SMA
# SPY2 %>%
    ggplot(aes(x = date, y = close)) +
    geom_line() +           # Plot stock price
    geom_bbands(aes(high = high, low = low, close = close), SMA.close) +
    coord_x_date(xlim = c(today() - years(1), today()), ylim = c(80, 130))


```



Sources:

Went through a lot of the quantmod documentation to find this info paired with the financial analysis I have been trying to teach myself. 

https://cran.r-project.org/web/packages/quantmod/index.html )

 mutate_fun = SMA, n = 15) %>%

# 
# # SMA
# AAPL %>%
#     ggplot(aes(x = date, y = close)) +
#     geom_line() +           # Plot stock price
#     # geom_bbands(aes(high = high, low = low, close = close), ma_fun = SMA, n = 50) +
#     coord_x_date(xlim = c(today() - years(1), today()), ylim = c(80, 130))
# 

```



Sources:

Went through a lot of the quantmod documentation to find this info paired with the financial analysis I have been trying to teach myself. 

https://cran.r-project.org/web/packages/quantmod/index.html 