---
title: "Comparison of Like-Minded Companies"
author: "Tim Potter"
date: "April 2, 2019"
output: html_document
---


Gets us the packages that we need to get the data.
We are using the Quantmod library as of now

```{r}
#install.packages("tidyquant", repo="http://cran.us.r-project.org")
#install.packages("quantmod")
#install.packages("quadprog", repo="http://cran.us.r-project.org")
#install.packages("forecast", repo="http://cran.us.r-project.org")
library(quantmod)
library(ggplot2)
library(plotly)
library('forecast')
```


The start and endates for these samples. It pulls data based on the day. I need to see if it is possible to find stuff for intraday trading, but this helps us get started for now. 


```{r}
#Define start and End dates
start <- as.Date("2018-01-01")
end <- as.Date("2019-04-02")
```

Get some of the symbols that we will be looking at in the timefram that we are looking at. 

```{r}
#?getSymbols

AMD2 <- getSymbols("AMD", src = "yahoo", from = "2017-01-01", to = "2019-04-20", auto.assign = FALSE)

#I tried to add SOX but it failed, I might have the symbol wrong...
getSymbols(c("AAPL", "AMD", "SPY", "MU", "NVDA"), src="yahoo", from = start, to = end)
```

I'm going to compare two companies, Nvidia and AMD. These two companies are two of the top compeitors in the GPU manufacturing market. Behind Intel, these two are the closest in competition here. We're going to look at the stock prices to see what kind of effect the cryptocurrency boom had on the two companies, and why. More specifically , we'll look at the stock prices from July 2018 to January 2019. 
Here is a candlestick for Nvidia, and one for AMD.

```{r nvidia}

candleChart(NVDA, up.col = "green", dn.col = "red", theme = "white")
candleChart(AMD, up.col = "green", dn.col = "red", theme = "white")
```


Now lets take a look at Nvidia over the last month, and compare them with their major competitor in the GPU field, AMD.

```{r NVDA AMD}
start <- as.Date("2019-03-01")
end <- as.Date("2019-04-01")
getSymbols(c("AMD", "NVDA"), src="yahoo", from = start, to = end)
candleChart(NVDA, up.col = "green", dn.col = "red")
candleChart(AMD, up.col = "green", dn.col = "red")
```

A little longer look at the comparison of the two companies.

NVidia RTX 2080 released 9-10-2018
AMD Radeon VII released 2-7-2019
```{r longterm}
start <- as.Date("2017-01-01")
end <- as.Date("2019-04-01")
getSymbols(c("AMD", "NVDA"), src="yahoo", from = start, to = end)
lineChart(NVDA, theme = "white.mono")
#addTA(OpCl(NVDA),col='blue', type='h') 
lineChart(AMD, theme = "white.mono")
#addTA(OpCl(AMD),col='blue', type='h') 
```

As you can see here, both companies experienced a rather steep rise in their stock prices, followed by a just as steep fall. Why both of these companies would experience such a dramatic shift at the same time may not be readily apparent, but it will when we take a look at another stock that had a drastic change on the GPU market. 
Let's compare this to the rise of another important stock, Bitcoin.
```{r bitcoin}
getSymbols("BTC-USD", src="yahoo", from = start, to = end)
str(`BTC-USD`)
lineChart(`BTC-USD`, theme = "white.mono")
#addTA(OpCl(`BTC-USD`),col='blue', type='h') 
```

Bitcoin's spike in late 2017 brought a whole field og crypto currencies into prominence. The sudden profitability in mining these currencies led to the increase of miners, from people mining on their home computers to large firms running dozens of machines at a time. These miners found that gaming-oriented GPUs were necessary to get enough processing power to turn a profit in the business. And so, large quantities of GPUs were bought, wrecking the Supply and Demand balance of the market. It only got worse as miners needed to increase their power to keep up with the ever increasing difficulty of crypto mining. This prolonged time of  mining viablility is a very probable reason we see Nvidia and AMD increase so much over that time span. In fact, Nvidia reported that they made $289 million in revenue from crypto-specific GPUs in the first quarter of 2018. 

What happened next? 
The bubble popped. Many miners found that they could no longer make enough to turn a profit. As a result, the demand dried up. The driven-up prices of all the graphics cards still on the market didn't correct nearly fast enough. And so there was a large sell-off of both companies shares and a big dip in the stock price.
From Coin Telegraph, 12-22-2018, https://cointelegraph.com/news/following-crypto-mining-crash-gpu-producer-nvidia-worst-performer-in-sp-500
    
    The drastic decrease in crypto mining profitability has hit graphics processing unit (GPU) producers like Taiwan-based Nvidia hard. In Q4 2018, the firm experienced a massive sell-off of its shares, cutting the stock price by 54 percent and making it the worst performer in the S&P 500, CNBC reports on Dec. 21.
    
    From 2016 to September 2018, Nvidia's market value markedly increased from $14 billion to $175 billion as demand for its GPUs in artificial intelligence (AI) and cryptocurrency mining grew. In May, the firm reported its profits from crypto mining for the first time while forecasting a two-thirds drop in sales to miners for Q2.
    
    Nvidia initially forecasted insignificant crypto mining-related sales in Q3, while the quarterly report in November revealed that GPU sales for blockchain-related applications had all but disappeared. Nvidia CEO Jensen Huang said that the company's "near-term results reflect excess channel inventory post the cryptocurrency boom, which will be corrected."
    
    The disappearance of crypto-related sales has left the company with a "crypto hangover," according to Huang. The cryptocurrency frenzy drove up prices for Nvidia's GPUs, but once that demand disappeared, prices did not decrease quickly enough to attract customers who were waiting for more affordable cards.
    
    In addition to the decrease in crypto mining sales, Nvidia's data center segment failed to meet Wall Street expectations, even though revenue grew by 58 percent, per CNBC. Today, Nvidia stock is down 4.09 percent, closing at $129.57.
    
    Chip stocks overall have performed poorly this year. The PHLX Semiconductor Index, which tracks major hardware producers like Nvidia and Advanced Micro Systems (AMD) is down 20.37 percent over the last three months. AMD's share price is down 45.42 percent over the same period.
    
    The post-mining boom hardware glut has seen a notable drop in prices. AMD's popular Radeon RX580 graphics processing unit (GPU), which has been widely used by crypto miners, is now being sold for $180, down 67 percent from a peak average price around $550 in February 2018.
    
    Decreased profitability in the current bear market has caused some miners to leave the business. Some mining firms in China have been selling off dated hardware that has reached its shutdown price by the kilogram in order to mitigate their losses. According to local reports, earnings from mining are no longer enough to cover electricity and other associated costs.

Let' try looking at the two companies from July, 2018 through January , 2019. This goes from the great hike in stock prices through the collapse of the crypto market, and into each companies recovery.

```{r 6 months}
start <- as.Date("2018-07-01")
end <- as.Date("2019-01-01")
#?candleChart
getSymbols(c("AMD", "NVDA"), src="yahoo", from = start, to = end)
candleChart(NVDA, AMD, theme = "white", TA = NULL)
#addTA(OpCl(NVDA),col='blue', type='h') 
candleChart(AMD, theme = "white", TA = NULL)
#addTA(OpCl(AMD),col='blue', type='h') 

stocks <- as.xts(data.frame(nv = NVDA$"NVDA.Close", amd = AMD$"AMD.Close"))

plot(as.zoo(stocks$"NVDA.Close"),screens = 1,lty = 1,main="Closing Prices of Nvidia, AMD", col = "red" ,xlab = "Date, July 2018 - January 2019",ylab = "Close Price, USD") 
#  geom_vline(xintercept = as.Date("2018-09-01"), size=0.5, linetype="dotted")
par(new = TRUE)
plot(as.zoo(stocks$"AMD.Close"),screens = 1,lty = 2,col = "blue" ,xlab = "",ylab = "", xaxt = "n", yaxt = "n")
abline(v = as.Date("2018-09-01"), lty = 2)
axis(4)
mtext("Price", side = 4, line = 3)
legend("topleft",c("Nvidia(left)","AMD(right)"),lty = c(1,2),cex = 0.5)
```


Now let's try comparing game companies, like Microsoft, Sony, Nintendo.

Specifically, we'll take a look at the stock prices of each company around the release of the three newest consoles: the PS4 Pro, Xbox One X, and Nintendo Switch.

PS4 Pro: 11-10-16

Xbox One X: 11-7-17

Nintendo Switch: 3-3-17

Let's take a look at the stock fluctuations from the beginning of 2016 to the end of 2018.
```{r get consoles}
start <- as.Date("2016-01-01")
end <- as.Date("2018-12-31")

getSymbols(c("MSFT", "SNE", "NTDOY"), src="yahoo", from = start, to = end)
candleChart(MSFT, up.col = "green", dn.col = "red", theme = "white")
candleChart(SNE, up.col = "green", dn.col = "red", theme = "white")
candleChart(NTDOY, up.col = "green", dn.col = "red", theme = "white")
```

Now let's look more closely  here, with 30 days before and after the release of each console for each company.

```{r close consoles}
sPro <- as.Date("2016-10-10")
ePro <- as.Date("2016-12-10")

sX <- as.Date("2017-10-7")
eX <- as.Date("2017-12-7")

sSwitch <- as.Date("2017-2-3")
eSwitch <- as.Date("2017-4-3")

#Candle charts around the release of the Pro
getSymbols(c("MSFT", "SNE", "NTDOY"), src="yahoo", from = sPro, to = ePro)
candleChart(MSFT, up.col = "green", dn.col = "red", theme = "white")
candleChart(SNE, up.col = "green", dn.col = "red", theme = "white")
candleChart(NTDOY, up.col = "green", dn.col = "red", theme = "white")

#Candle charts around the release of the X
getSymbols(c("MSFT", "SNE", "NTDOY"), src="yahoo", from = sX, to = eX)
candleChart(MSFT, up.col = "green", dn.col = "red", theme = "white")
candleChart(SNE, up.col = "green", dn.col = "red", theme = "white")
candleChart(NTDOY, up.col = "green", dn.col = "red", theme = "white")

#Candle charts around the release of the Switch
getSymbols(c("MSFT", "SNE", "NTDOY"), src="yahoo", from = sSwitch, to = eSwitch)
candleChart(MSFT, up.col = "green", dn.col = "red", theme = "white")
candleChart(SNE, up.col = "green", dn.col = "red", theme = "white")
candleChart(NTDOY, up.col = "green", dn.col = "red", theme = "white")
```

What conclusions can we draw from this?


```{r arima}
arimaData <- auto.arima(SNE$SNE.Close)

chartSeries(as.ts(SNE$SNE.Close))
lines(fitted(arimaData), col='red')
```