---
title: "Proposal"
author: "cyber-atlas"
date: "April 2, 2019"
output: html_document
---


Gets us the packages that we need to get the data.
We are using the Quantmod library as of now

```{r}
#install.packages("tidyquant", repo="http://cran.us.r-project.org")
#install.packages("quantmod")
library(quantmod)
library(ggplot2)
library(plotly)
```


The start and endates for these samples. It pulls data based on the day. I need to see if it is possible to find stuff for intraday trading, but this helps us get started for now. 


```{r}
#Define start and End dates
start <- as.Date("2018-01-01")
end <- as.Date("2019-04-02")
```

Get some of the symbols that we will be looking at in the timefram that we are looking at. 

```{r}
#?getSymbols

AMD2 <- getSymbols("AMD", src = "yahoo", from = "2017-01-01", to = "2019-04-20", auto.assign = FALSE)

#I tried to add SOX but it failed, I might have the symbol wrong...
getSymbols(c("AAPL", "AMD", "SPY", "MU", "NVDA"), src="yahoo", from = start, to = end)
```
<br> We ran into issues getting SOX to import, I probably goofed and got the wrong symbol. 



The data is saved as an xts object. From what I could tell it is very similar to a dataframe except it has more fields. Also showing some of the data.

```{r}
class(AMD)

head(AMD)
tail(AMD)

head(SPY)
tail(SPY)

head(MU)
tail(MU)

names(MU)

head(NVDA)
tail(NVDA)

```

Let's plot the stock data

The close prices of Apple over the given timeframe
```{r}

plot(AAPL[, "AAPL.Close"], main = "AAPL")
```

Another way to plot, this time using the AMD close prices
```{r}
amd.df<- data.frame(AMD)

ggplot(AMD, aes(x=index(AMD), y=AMD[,6]))+geom_line(color="black")+scale_x_date(date_labels = "%b %y", date_breaks = "6 months")

```


Line charts are great and all but candlestick charts are more used and more useful.

This is the candle stick chart for MU 

```{r}

candleChart(MU, up.col = "green", dn.col = "red", theme = "white")

```

Here is a candlestick for Nvidia, and one for AMD.

```{r nvidia}

candleChart(NVDA, up.col = "green", dn.col = "red", theme = "white")
candleChart(AMD, up.col = "green", dn.col = "red", theme = "white")
```


Now lets take a look at Nvidia over the last month, and compare them with their major competitor in the GPU field, AMD.

```{r NVDA AMD}
start <- as.Date("2019-03-01")
end <- as.Date("2019-04-01")
getSymbols(c("AMD", "NVDA"), src="yahoo", from = start, to = end)
candleChart(NVDA, up.col = "green", dn.col = "red")
candleChart(AMD, up.col = "green", dn.col = "red")
```

A little longer look at the comparison of the two companies.

NVidia RTX 2080 released 9-10-2018
AMD Radeon VII released 2-7-2019
```{r longterm}
start <- as.Date("2015-03-01")
end <- as.Date("2019-04-01")
getSymbols(c("AMD", "NVDA"), src="yahoo", from = start, to = end)
candleChart(NVDA, up.col = "green", dn.col = "red", theme = "white")
candleChart(AMD, up.col = "green", dn.col = "red", theme = "white")
```

Let's compare this to the rise of another important stock, Bitcoin.
```{r bitcoin}
getSymbols("BTC-USD", src="yahoo", from = start, to = end)
candleChart(`BTC-USD`, up.col = "green", dn.col = "red", theme = "white")
```


Now let's try comparing phone companies, like Apple, Samsung, etc.

```{r get phones}
start <- as.Date("2018-01-01")
end <- as.Date("2019-04-02")

getSymbols(c("MSFT", "SNE", "NTDOY"), src="yahoo", from = start, to = end)
candleChart(MSFT, up.col = "green", dn.col = "red", theme = "white")
candleChart(SNE, up.col = "green", dn.col = "red", theme = "white")
candleChart(NTDOY, up.col = "green", dn.col = "red", theme = "white")