---
title: "FinalReport"
author: "cyber-atlas"
date: "5/5/2019"
output: html_document
---


Tell the story, not only the coding
The total number of figures and tables should not exceed 10. Include only the most interesting results, and condense information in each figure.
Each figure, table, or analysis must be accomanied by explanatory text.
The project report should include a personal contribution section. Each teammate will write a paragraph about his/her own contribution to the team.
An optional survey for comments on the contributions of your teammates will be sent out.


Report is due on 12:00pm, May 6 sharp
Each team should push to GitHub by the deadline, and the coordinator will email the instructor the link to their GitHub repo.
If feasible, each team please also bring a color printed copy
All sources need to be cited, which includes data source, blog posts, tutorials that include codes, etc. R help document does not need to be cited.

```{r setup}
library(quantmod)
library(ggplot2)
library(plotly)
library('forecast')
```


# Stock Analysis With R 

### The Motivation

Nowadays it seems like there is a renewed attention in the stock market and investing in general. It seems like everyday you hear more and more about something a company did and how it will be the downfall of the company. The very next week, the same people that were predicting the downfall of the company, are talkng about how it's undervalued and its price is going to soar. Demonstrating to us that even the experts really don't know for sure.  

The renewed interest in the market is even evident among millenials, as demonstrated by the explosion of mobile investing apps. There's a range of them that are made to appeal to people with a wide variety of financial knowledge/experience. 

Robinhood is by far the most popular app as it offers free stock and options trading. However, Robinhood does not come with the advanced news and charting features that paid competitiors such as Think or Swim come with.

Betterment is also another popular investment app. It takes a fee, but generally it is much smaller than what a traditional broker would charge. Betterment does not allow users to purchase individual stocks. Instead, the user contributes money to the app, and an algorithm allocates the money into mutual funds taking into account the amount of risk the user says they're willing to take. 

Consequently that led us to explore the following questions:
 
* Do the news stories about companies actually affect the price of a stock? Knowing this could help one make the decision whether or not to listen to the news, and whether or not they should use a tool that gives them more insght on the news surrounding a stock than Robinhod. 
 
* Does the value of a commodity affect the price of stocks in a similar market space? Knowing this could help a user make the decision whether or not to use Robinhood, or an app that allows for more streamlined comparisons of stocks. 

* Do popular technical indicators actually work? Knowing this could help one make the decision on whether or not they want to use Robinhood or an app that allows them to use to technical indicators to help predict value.

* How does company performance compare to their Stock Price? This cwould be interesting to see to determine how much weight to put on the news about them, and in determining the feasability of using an algorithm to manage your money. 

* Can we predict the price of a stock on a future date? There are strong arguments on both sides of this question, so we decided to test it for ourselves and draw our own conclusions. 

### The Datasets 
<br>
The datasets we used in this investigation were obtained from Yahoo Finance using the quantmod package and from the _____________________ Kaggle dataset. The link to the datasets are below. 

[Yahoo Finance](https://finance.yahoo.com/)

[Quantmod Information](https://cran.r-project.org/web/packages/quantmod/index.html)

## TODO Add the kaggle dataset name and link above 

### The Analysis

## TODO Add the airplane stuff talking about news

## TODO Add the Bitcoin AMD NVIDIA stuff talking aobut how important it is to be able to compare assets and stock prices

We wanted to take a look at two competing companies, Nvidia and AMD, and see what happened to their stock prices when outside forces impacted their marketplace. The outside force chosen here was the shortage of GPUs do to the rise in cryptocurrency mining in the first half of 2018.

The process of mining cryptocurrency involves solving increasingly complex calculations on a machine in order to generate new coins and to uodate the blockchain that serves as the currency ledger. As a currency matures, miners need increasingly more powerful mining rigs with enough processing power to generate a profit from the coins. When Bitcoin and other cryptocurrencies became truly lucrative in 2017, the large influx in miners led to a dramatic increase in the demand for Nvidia and AMD GPUs. The law of Supply and Demand took over, and the selling price of most of the GPUs on the market skyrocketed, in some cases double the MSRP. 

At the beginning, this increase in sales led to a spike in the stock prices of both companies. However, the lack of supply and a decrease in the demand from the mining sector soon proved to be a problem. 

The end of summer 2018 saw a massive decrease in the demand for new GPUs from coin miners. The cost of coninuously mining cyrptocureency had overcome the profit turned from the mining, and many left the scene. The problem for Nivdia and Amd here was that the prices of the GPUs on the market could not correct themselves fast enough to keep up with the decrease in sales. As a result, no one could or would buy their products. This led to the stock price for each company to plummet. From September to November, shares fell for both companies. Nvidia managed to los 54% of their stock value in Q4 of 2018 alone. 


```{r NVDA AMD}
start <- as.Date("2018-07-01")
end <- as.Date("2019-01-01")

getSymbols(c("AMD", "NVDA"), src="yahoo", from = start, to = end)


stocks <- as.xts(data.frame(nv = NVDA$"NVDA.Close", amd = AMD$"AMD.Close"))

plot(as.zoo(stocks$"NVDA.Close"),screens = 1,lty = 1,main="Closing Prices of Nvidia, AMD", col = "red" ,xlab = "Date, July 2018 - January 2019",ylab = "Close Price, USD") 
#  geom_vline(xintercept = as.Date("2018-09-01"), size=0.5, linetype="dotted")
par(new = TRUE)
plot(as.zoo(stocks$"AMD.Close"),screens = 1,lty = 2,col = "blue" ,xlab = "",ylab = "", xaxt = "n", yaxt = "n")
abline(v = as.Date("2018-09-01"), lty = 2)
axis(4)
mtext("Price", side = 4, line = 3)
legend("topleft",c("Nvidia(left)","AMD(right)"),lty = c(1,2),cex = 0.5)
```

This grpah shows the stock prices for Nvidia and AMD from July, 2018 to January, 2019. We can see the fluctuation in the stock prices for both companies here. Since the share price for Nvidia is much higher than that of AMD, each line is scaled individually on the graph. From here, we can clearly see the correlation between the decline in cryptocurrency mining and the drop in the stock prices. 

### Testing the Effectiveness of Bollinger Bands

Given that Robinhood does not have technical indicators, I wanted to test the effectiveness of Bollinger Bands to see if they really work. If they don't work, then it's no issue that Robinhood does not have them. If they do, then it might be worth looking at a different platform. 

Bollinger Bands work based on the moving average, meaning that the oldest value is dropped when a new one is added. The top band is 1 standard deviation above the moving average, the middle band is the moiving average, and the bottom band is 1 standard deviation below the moving average. 

A popular strategy is to sell or enter a position that profits from a stock decreasing when the price goes down hitting the moving average. 

To test this we decided to use the following code to highlight everytime the stock dips below the moving average. To give us a conceptual visual understanding of what we are looking at. 

## TODO get the chart with the highlights added here 

We see here that often when the stock dips, that it rebound within a day or so. This is a bit misleading because we are looking at the stocks on a day by day timeframe. However, the market reacts much faster and even the times that it dips and rebounds, traders can make money. 

## TODO put in the table

We also see that there are dips that are pretty significant. The largest dip was 13% as well as numerous other dips greater than 1%. This may not seem like a lot, but it is significicant given that banks often only give fractions of a percent in interest. Here we found that the mean percenage is 2.45% which is much greater. 

Paired with the fact that traders can make moeny on the dips that have a good rebound, it is safe to say that Bollinger Bands work. Thus having them would be useful, and usrers should explore other trading platforms that allow them to use technical indicators. 


## TODO Add the stuff about comparing company performance vs stock price

## TODO Add the stuff about predictng future stock price algorithmically

There are a lot of factors that contribute the price of a stock and how it moves. Given the growing popularity of algorithmic apps such as Betterment, I wanted to see if it was possible to predict the price the future price of a stock. 

This results would allow users to decide for themselves as to whether or not they want to invest their money on a platform that is not traded by humans. 

### Our Conclusion

## TODO Add the overall reflection

### Our Sources

https://cointelegraph.com/news/following-crypto-mining-crash-gpu-producer-nvidia-worst-performer-in-sp-500
http://rstudio-pubs-static.s3.amazonaws.com/265813_dab79c8eb62d41e381a7e230465573ab.html


## Add the sources

## TODO Alex Add reflection

## TODO Blake add reflection

## TODO Sam add reflection

## TODO Tim add reflection

My contribution to the project was the comparison between Nvidia and AMD. It wasn't the most in-depth or difficult analysis, but I was able to graph the stock prices for each company over time. Then, since I had prior knowledge of the Bitcoin blowup and the effect it had on Nvidia GPUs, I decided to look into what happened to each companies stocks over that specific timeframe. I actually found pretty much exactly what I expected - there was a very noticiable impact on both companies performances on the market. 

Since we didn't have any more time, both in the presentation and just in the class itself, I wasn't able to take the exploration much further. However, I do find the plenty interesting, and I think that I will look into stuff like this more in my own time later. 