---
title: "Proposal"
author: "cyber-atlas"
date: "April 2, 2019"
output: html_document
---


Gets us the packages that we need to get the data.
We are using the Quantmod library as of now

```{r}
install.packages("quantmod")
library(quantmod)
```


The start and endates for these samples. It pulls data based on the day. I need to see if it is possible to find stuff for intraday trading, but this helps us get started for now. 


```{r}
#Define start and End dates
start <- as.Date("2018-01-01")
end <- as.Date("2019-04-02")
```

Get some of the symbols that we will be looking at in the timefram that we are looking at. 

```{r}
?getSymbols
#I tried to add SOX but it failed, I might have the symbol wrong...
getSymbols(c("AAPL", "AMD", "SPY", "MU"), src="yahoo", from = start, to = end)
```
<br> We ran into issues getting SOX to import, I probably goofed and got the wrong symbol. 



The data is saved as an xts object. From what I could tell it is very similar to a dataframe except it has more fields. Also showing some of the data.

```{r}
class(AMD)

head(AMD)
tail(AMD)

head(SPY)
tail(SPY)

head(MU)
tail(MU)

```
